Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Different Restaurant Cuisines and Prices

### 2024-04-19 paper/paper.qmd
Reflect title change in the paper

---
title: "Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Restaurant Cuisines and Prices"
author: 
  - Moohaeng Sohn
thanks: "Code and data are available at: [https://github.com/alexsohn1126/yelp-analysis](https://github.com/alexsohn1126/yelp-analysis)"
date: today
date-format: long
abstract: "We use the Yelp dataset to explore and model how different attributes of a restaurant play a factor in the review ratings. We found there are some variables which are promising predictors for the rating of a restaurant. Cuisines such as Chinese or Mexican tended to have lower ratings, and lower priced cuisines performed worse. This study can be used to predict whether a restaurant will be successful or not."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Different Restaurant Cuisines and Prices"
author: 
  - Moohaeng Sohn
thanks: "Code and data are available at: [https://github.com/alexsohn1126/yelp-analysis](https://github.com/alexsohn1126/yelp-analysis)"
date: today
date-format: long
abstract: "We use the Yelp dataset to explore and model how different attributes of a restaurant play a factor in the review ratings. We found there are some variables which are promising predictors for the rating of a restaurant. Cuisines such as Chinese or Mexican tended to have lower ratings, and lower priced cuisines performed worse. This study can be used to predict whether a restaurant will be successful or not."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
